---
title: "Queens, A Borough For A Family"
output: html_document

---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(lubridate)
Perm_event <- read_csv("https://data.cityofnewyork.us/resource/tvpp-9vvx.csv?$limit=50000")
Restaurant <- read_csv("https://data.cityofnewyork.us/resource/43nn-pn8j.csv?$limit=50000")
knitr::opts_chunk$set(fig.width = 5, fig.asp = 1/3,echo = FALSE)
```

## New York Boroughs

New York is one of the most popular and famous places in the world. Some of the many things the state is known for are its food and countless activities. When looking for a place to live, these are important qualities that a person of any age would care about. Below, I have done the research for you. I am going to dive into the hard data behind New York's restaurant and event life with a little bit of my own person opinions being a current resident in Manhattan. With this data, I am going to provide detail into why Queens is best borough to live in for a new family! 

Lets get started by taking a look below at the average length of events which have taken place in each borough over the past few months. 

### What is the average length of events per borough?

```{r echo=FALSE}
Perm_events1 <- Perm_event%>%
  mutate(Perm_event,length_event_hr=hour(end_date_time)-hour(start_date_time),
         length_event_day=day(end_date_time)-day(start_date_time))
by_borough <- group_by(Perm_events1,event_borough)
avg_lengths <- summarise(by_borough,
                        count=n(),
                        length=mean(length_event_hr,na.rm = TRUE))

ggplot(data=avg_lengths,mapping=aes(x=event_borough,y=length))+
  geom_point()+
  labs(title = "Longest average events take place in Brooklyn")

```

Here, as you can see, the longest average length of events take place in the Brooklyn borough. The second borough with the longest average event time span is Queens. This is the perfect place to be for a new family because they don't want the events going on too long but to last a few hours in order to check them out. Queens has an average event length of about 6 hours. This is plenty of time for one to bring their family to check out for an hour, or for someone interested in checking out what is happening in their neighborhood as an adventure! 

### By borough, which ones have the most options for restaurants?

```{r}
by_boroughs <- group_by(Restaurant,boro)
sum_cuisines <- summarise(by_boroughs,
                        count=n())
          
ggplot(data=sum_cuisines,mapping=aes(x=boro,y=count))+
  geom_boxplot()+
  labs(title = "Most cuisine options are in Manhattan")              
```

Manhattan, as one could assume, has the most options for different types of cuisines and number of restaurants, placing Queens close to second after Brooklyn. As someone who lives in Manhattan on the Upper West Side at the moment, and as I'm sure you know, the city is always pretty noisy. With this conclusion, I would recommend Queens as a great place for a family to live because there are still such a large number of cuisine options there with the benefit of not too many, leading to a noisy neighborhood and a newborn not being able to sleep.

### When are events taking place in each borough?

```{r}
Perm_event_date <- Perm_event%>%
  separate(start_date_time, into = c("date","time"),sep = " ")%>%
  mutate(wday=wday(date,label = TRUE,abbr = FALSE))%>%
  select(event_name,date,wday,event_type,event_borough)

by_date <- group_by(Perm_event_date,event_borough,wday)
sum_date <- summarise(by_date,count=n())

sum_date%>%
  mutate(wday=recode_factor(wday,
                             Monday= "Weekday",
                             Tuesday= "Weekday",
                             Wednesday= "Weekday",
                            Thursday="Thursday",
                            Friday="Weekend",
                            Saturday="Weekend",
                            Sunday="Weekend"))%>%
  group_by(event_borough,wday)%>%
  summarise(count=sum(count))%>%
  ggplot(aes(fill=wday, y=count, x=event_borough)) + 
    geom_bar(position="dodge", stat="identity")
  
```


## Conclusion


