---
title: "Restaurant Event Dashboard"
output: html_document

---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(lubridate)
Perm_event <- read_csv("https://data.cityofnewyork.us/resource/tvpp-9vvx.csv")
Restaurant <- read_csv("https://data.cityofnewyork.us/resource/43nn-pn8j.csv")
knitr::opts_chunk$set(fig.width = 5, fig.asp = 1/3)
```

## New York Boroughs

New York is one of the most popular and famous places in the world. Some of the many things the state is known for are its food and many activities. When looking for a place to live, these are important qualities that a person of any age would care about. Below, I have done the research for you. I am going to dive into the hard data behind New York's restaurant and events life with a little bit of my own person opinions being a current resident in NYC. With this data, I am going to provide detail into which of the five boroughs is best to live in depending on who you are! 

Lets get started by taking a look below at the average length of events which have taken place in each borough over the past few months. 

### What is the average length of events per borough?

```{r}
Perm_events1 <- Perm_event%>%
  mutate(Perm_event,length_event_hr=hour(end_date_time)-hour(start_date_time),
         length_event_day=day(end_date_time)-day(start_date_time))
by_borough <- group_by(Perm_events1,event_borough)
avg_lengths <- summarise(by_borough,
                        count=n(),
                        length=mean(length_event_hr,na.rm = TRUE))

ggplot(data=avg_lengths,mapping=aes(x=event_borough,y=length))+
  geom_point()+
  labs(title = "Longest average events take place in Brooklyn")

```

Here, as you can see, the longest average length of events take place in the Brooklyn borough. The second borough with the longest average event time span is Queens. I think that this is the perfect place to be for the reason that you do not want the events going on in your area to be too long but you also do not want them to be too short. Queens has an average event length of about 6 hours. This is plenty of time for one to bring their family to check out for an hour, or for someone interested in checking out what is happening in their neighborhood as an adventure! 

### By borough, which ones have the most options for restaurants?

```{r}
by_boroughs <- group_by(Restaurant,boro)
sum_cuisines <- summarise(by_boroughs,
                        count=n())
sum_cuisines
                        
ggplot(data=sum_cuisines,mapping=aes(x=boro,y=count))+
  geom_boxplot()+
  labs(title = "Most cuisine options are in Manhattan")
```

### When are events taking place in each borough?

```{r}
Perm_event_date <- Perm_event%>%
  separate(start_date_time, into = c("date","time"),sep = " ")%>%
  mutate(wday=wday(date,label = TRUE,abbr = FALSE))%>%
  select(event_name,date,wday,event_type,event_borough)

Perm_event_date

by_date <- group_by(Perm_event_date,event_borough,wday)
sum_date <- summarise(by_date,count=n())

sum_date%>%
  mutate(wday=recode_factor(wday,
                             Monday= "Weekday",
                             Tuesday= "Weekday",
                             Wednesday= "Weekday",
                            Thursday="Thursday",
                            Friday="Weekend",
                            Saturday="Weekend",
                            Sunday="Weekend"))


  
```

## Conclusion


